Technical Interview

### 2017-09-04 tex/paper/paper.tex
paper final
final paper this time

The aim was to keep the software as simple as possible while targeting a
good design and performance. 
The right balance is always difficult to achieve as unfortunately no 
software is ever perfect.

The code is documented while we believe that a simple and well organised
code needs less documentation. The complexities are presented in the key
area of the code.

@@

We can run the automated as described in  \autoref{fig:tests} with the command:
\begin{verbatim}
time cabal test --show-details=streaming
\end{verbatim}
\begin{figure}[h!]
\begin{center}
\includegraphics[width=1\textwidth]{img/tests.png}
\caption{Automated Testing}
\label{fig:tests}
\end{center}
\end{figure}

@@

\subsection{Analytics Testing} 
These are the unit tests for the Analytics only.
\begin{description}
	\item [CDF creation]
		Given a 1000 pseudo random PDF, we ensure 
		that the last pillar of the CDF is 1.
		As the CDF is build incrementally, this gives a good sense that
		the CDF construction has been correct.
	\item [InverseCDF, CDF and PDF pillars check]
		Given a 1000 pseudo random PDF, we ensure that
		the pillars on the x axis of the PDF and CDF are the pillars on the y
		axis of the Inverse CDF.
	\item [PDF Stable]
		Given a 1000 pseudo random PDF pillars, 
		we ensure that we get the same PDF given the reverse input.
	\item [PDF consistency]
		Given a 1000 pseudo random PDF, 
		we ensure that the sum of the PDF pillars probabilities are 
		equal to 1. We indeed modelise the non selected element
		only in the CDF.
	\item [Inverse CDF valid]
		Given a 1000 pseudo random PDF,
		we build the CDF and we ensure that for a random number of
		x values within 0 and 1 we always recover a x pillars of the PDF.
	\item [PDF failure]
		We test the expecture failure of the PDF construction. 
		We can't have negative values. We need at least one valid pillar.
		The pillars with 0 probabilities are discarded.
		And the sum of the PDF pillars probabilities must be 
		equal to one.
	\item [Inverse CDF Failure]
		We check that the inverse CDF function raise an
		exception if the x input is outside the correct bounds, 
		$\left[0, 1\right]$.
	\item [Mean and Standard Deviation Failure]
		These functions raise an exception for empty lists.
		We test it automatically.
	\item [PDF and Inverse CDF Non Regression]
		We ensure without randomness that given a set of pillars,
		we recover the expected Inverse CDF and PDF.
\end{description}
\subsection{Uniform Engine Testing}

@@

\begin{description}
	\item [Mean and Standard Deviation]
		Given a large number of random number generated for
		both Ecuyer and Mersenne, i.e. $100000$.
		We ensure that the mean and the standard deviation 
		of the distributions are still the same. Run 10 times.
		We ensure that the uniform random number engines keep
		the same properties.
	\item [Bounds]
		Test ensuring that the uniform pseudo random generators
		generate probabilities with the $[0, 1]$ bound.
		Run $10$ times for $1000000$ random numbers.
	\item [Uniform]
		Ensure that the ditributions generated are uniform,
		by making sure that we match a flat distribution at 0.001
		precision on the standard deviation of the difference
		between the PDFs.
		Run 10 times for $100000$ random numbers.
	\item [Performance]
		Ensure that the pseudo random numbers keep at
		least the same performance.
		Run 10 times for $100000$ random numbers.
\end{description}

@@

%-------------------------------------------------------------------------------
\section{Possible Extensions}
Here is a list of possible extension we could add.
\begin{description}
	\item [Analytics]
	Further abstract the PDF, CDF, InvCDF to handle all kind of keys.
	\item [Testing]
	We could run the tests on different environments to ensure the portability of 
	the code.
	\item [UI] 
	A nice extension would be to add a Graphic User Interface,
	using the library 
	\href{https://hackage.haskell.org/package/threepenny-gui}{threepenny-gui}
	to create a portable Web application.

>>>>

The aim was to keep the software as simple as possible while targeting a
good design and performance.

The code is documented while we believe that a simple and well organised
code needs less documentation. The complexities are presented in the some
area of the code.

@@

We can run the automated as described in  \autoref{fig:tests} with the command:
\begin{verbatim}
time cabal test --show-details=streaming
\end{verbatim}
\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.7\textwidth]{img/tests.png}
\caption{Automated Testing}
\label{fig:tests}
\end{center}
\end{figure}

@@

\subsection{Analytics Testing} 
These are the unit tests for the Analytics only.
\begin{description}
	\item [CDF creation]
		Given a 1000 pseudo random PDF, we ensure 
		that the last pillar of the CDF is 1.
		As the CDF is build incrementally, this gives a good sense that
		the CDF construction has been correct.
	\item [InverseCDF, CDF and PDF pillars check]
		Given a 1000 pseudo random PDF, we ensure that
		the pillars on the x axis of the PDF and CDF are the pillars on the y
		axis of the Inverse CDF.
	\item [PDF Stable]
		Given a 1000 pseudo random PDF pillars, 
		we ensure that we get the same PDF given the reverse input.
	\item [PDF consistency]
		Given a 1000 pseudo random PDF, 
		we ensure that the sum of the PDF pillars probabilities are 
		equal to 1. We indeed modelise the non selected element
		only in the CDF.
	\item [Inverse CDF valid]
		Given a 1000 pseudo random PDF,
		we build the CDF and we ensure that for a random number of
		x values within 0 and 1 we always recover a x pillars of the PDF.
	\item [PDF failure]
		We test the expecture failure of the PDF construction. 
		We can't have negative values. We need at least one valid pillar.
		The pillars with 0 probabilities are discarded.
		And the sum of the PDF pillars probabilities must be 
		equal to one.
	\item [Inverse CDF Failure]
		We check that the inverse CDF function raise an
		exception if the x input is outside the correct bounds, 
		$\left[0, 1\right]$.
	\item [Mean and Standard Deviation Failure]
		These functions raise an exception for empty lists.
		We test it automatically.
	\item [PDF and Inverse CDF Non Regression]
		We ensure without randomness that given a set of pillars,
		we recover the expected Inverse CDF and PDF.
	\item [Statistics Non Regression]
		We ensure without randomness that given a set of pillars,
		we recover the expected statistics used in the post processing
		of the Stats engines.
\end{description}
\subsection{Uniform Engine Testing}

@@

\begin{description}
	\item [Mean and Standard Deviation]
		Given a large number of random number generated for
		both Ecuyer and Mersenne, i.e. $100000$.
		We ensure that the mean and the standard deviation 
		of the distributions are still the same. Run 10 times.
		We ensure that the uniform random number engines keep
		the same properties.
	\item [Bounds]
		Test ensuring that the uniform pseudo random generators
		generate probabilities with the $[0, 1]$ bound.
		Run $10$ times for $1000000$ random numbers.
	\item [Uniform]
		Ensure that the ditributions generated are uniform,
		by making sure that we match a flat distribution at 0.001
		precision on the standard deviation of the difference
		between the PDFs.
		Run 10 times for $100000$ random numbers.
	\item [Performance]
		Ensure that the pseudo random numbers keep at
		least the same performance.
		Run 10 times for $100000$ random numbers.
	\item [Engine Fail]
		Ensure that the construction of the engine 
		handles all the expected failure.
\end{description}

@@

%-------------------------------------------------------------------------------
\section{Possible Extensions}
Here is a list of possible extension we could add.
\begin{description}
	\item [Analytics]
	Further abstract the PDF, CDF, InvCDF to handle all kind of keys.

	Review the design of the statistics.
	\item [Testing]
	We could run the tests on different environments to ensure the portability of 
	the code.
	\item [UI] 
	A nice extension would be to add a Graphic User Interface,
	using the library 
	\href{https://hackage.haskell.org/package/threepenny-gui}{threepenny-gui}
	to create a portable Web application.
